Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-03-16 docs/ms.tex
Update ms.tex

The measurement of galaxy shapes from images is first step  of weak gravitational lensing analysis , since the observed ellipticities of distant galaxies are
Used to infer the shear map , which quantify how shape of galaxies are distorted.
The second step is to infer 
Finally,we can recover the projected mass profile of galaxies or dark energy by it’s shear map.

>>>>

The measurement of galaxy shapes from images is first step  of weak gravitational lensing analysis , since the observed ellipticities of distant galaxies are
Used to infer the shear map , which quantify how shape of galaxies are distorted.
The second step is to infer the shear map from galaxies ellipticity.Usually the estimate of g  involve simple or weighted
means of measured galaxy ellipticities.
Finally,we can recover the projected mass profile of galaxies or dark energy by it’s shear map.
